\RequirePackage[dvipsnames,svgnames]{xcolor} % Change font colors
\documentclass[%
  ngerman,        % (ngerman/english) internationalisation
%  listoffigures,  % optional listings of figures, tables and listings
%  listoftables,
%  listoflistings,
%  twoside,        % double sided layout
]{iib_thesis}

\newcommand{\missingQuote}{\textcolor{red}{\underline{\textbf{\uppercase{zitat fehlt}}}}}

% Add `diff` language for lstlisting
  \definecolor{diffstart}{named}{Grey}
  \definecolor{diffincl}{named}{Green}
  \definecolor{diffrem}{named}{OrangeRed}

  \lstdefinelanguage{diff}{
    basicstyle=\ttfamily\small,
    morecomment=[f][\color{diffstart}]{@@},
    morecomment=[f][\color{diffincl}]{+\ },
    morecomment=[f][\color{diffrem}]{-\ },
    numbers=left,
  }

\title{Entwicklung eines erweiterbaren Kommandozeileninterfaces zur Generierung von Web-Applikationen}
\author{Michael David Kuckuk}
\degree{Bachelor}
\studyprogram{Angewandte Informatik}
\date{\today}
\matno{108 017 207 503}
\firstadviser{Prof. Dr.-Ing. Markus König}
\secondadviser{Stephan Embers, M.\,Sc.}
\myabstract{
Modern web development relies highly on third-party dependencies, such as front-end frameworks or component libraries. Enabling all these dependencies to work together is often a tedious and repetitive task. Therefore, the goal of this work is to automate such initial creation of web projects.

In consideration of current approaches to this problem, a new command-line interface (CLI) tool will be created to guide the user through a small questionnaire, prompting them for their choice of tools and configurations. The questionnaire will both prevent the user from choosing unsupported configurations and provide them with additional helpful information about each question in order to remove entry barriers for new developers. The CLI will then create a new project according to the chosen specifications.

Using aspects of test-driven development, functional programming and graph theory, the implementation will focus on creating an extension-based framework for asking questions and installing dependencies. After also developing a small set of extensions to demonstrate the framework's capabilities, a series of end-to-end tests will be created and executed in order to judge the CLI's success. In the end, the created CLI will be able to successfully install a total set of 56 different configurations.
}

\interfootnotelinepenalty=10000 % Avoid footnotes splitting across pages

\begin{document}

  \input{acronyms}
  \input{intro}
%  \input{section_1}
%  \input{section_2}
  \input{stand_der_technik}
  \input{konzeptionierung}
  \input{implementierung}
  \input{evaluierung}
  \input{further_research}
  \input{fazit}

\end{document}
